Benchmarking Python Deep Learning Frameworks\\ for Language Modeling on GPUs

### 2016-12-14 paper/main.tex
added some tensorflow stuff

As discussed in section \ref{sec:benchmarks}, we found that DyNet was the fastest at performing our specific language modeling task. \lhl{TODO: flesh this out with a sentence or two more -- maybe something like ``DyNet seems to make certain optimizations that are advantageous in this setting''}

@@

\lhl{TODO: fill in other installation bits}

@@

\paragraph{TensorFlow}

@@

\subsubsection{Ease of use}
\ms{TF pro: Google has money and resources.}
\lhl{TODO: all the things that TensorFlow/DyNet support out of the box.
comment somewhere about documentation, debuggability}

\paragraph{DyNet}
DyNet includes built-in constructors for various NLP-relevant models, including several varieties recurrent neural nets like Tree LSTMs and encoder-decoders. THis makes it easy for the programmer to build many common kinds of models. DyNet also allows for dynamic computation graph, allowing nodes (representing parameter tensors) to be combined ``on the fly'' to adapt to, for example, data sequences of different lengths. While our neural language model used a static computation graph, DyNet made graph construction easy.

@@

\paragraph{TensorFlow} \textless TensorFlow stuff goes here \textgreater

>>>>

As discussed in section \ref{sec:benchmarks}, we found that DyNet was the fastest at performing our specific language modeling task. \lhl{TODO: flesh this out with a sentence or two more -- maybe something like ``DyNet seems to make certain optimizations that are advantageous in this setting''}
DyNet seems to make certain optimizations that are advantageous in this setting, perhaps specifically in the memory management choices it makes.\ms{is this okay?}

@@

@@

\paragraph{TensorFlow}
TensorFlow provides very extensive installation guidelines. It installs in the command line through pip, along with installing the dependencies. However, it rather inconveniently requires two different installations for GPU or CPU versions, which can cause issues if not using a virtual environment of some sort.

@@

\subsubsection{Ease of use}
\lhl{TODO: all the things that TensorFlow/DyNet support out of the box.
comment somewhere about documentation, debuggability\ms{Done?}}

\paragraph{DyNet}
DyNet includes built-in constructors for various NLP-relevant models, including several varieties recurrent neural nets like Tree LSTMs and encoder-decoders. This makes it easy for the programmer to build many common kinds of models. DyNet also allows for dynamic computation graph, allowing nodes (representing parameter tensors) to be combined ``on the fly'' to adapt to, for example, data sequences of different lengths. While our neural language model used a static computation graph, DyNet made graph construction easy.

@@

\paragraph{TensorFlow} TensorFlow is relatively easy to use, as it comes with a myriad of tutorials and examples. RNN support, as well as many other standard models, is relatively cutting-edge. Writing the computation graph requires some amount of know-how, since a lot if TensorFlow specific syntax; debugging the symbolic graph is hard since there are no values.
TensorFlow requires a decent amount of boilerplate code, specifically for mini-batching; the computation graph being static means that sequences either need to be padded, or mini-batches do, which can make computation somewhat cumbersome for RNNs. Overall, TensorFlow's large userbase, polyvalence and huge amounts of support from its creator (Google) makes up for its flaws.
